Project Contract\\Local Adaptive Optimization of Timestep

### 2013-11-05 report/contract.tex
Draft for final contract

\section{Learning Goals}
Course specific learning goals:
\begin{enumerate}
	\item Formulate an operational project plan.
	\item Search the relevant literature and write a literature review setting own work in perspective.
	\item Be able to formulate what plagiarism is, and demonstrate proper citation and reference style.
	\item Solve a selected problem of fair Computational and Mathematical Modelling / eScience content and difficulty.
	\item Produce a thorough experiment plan that clearly demonstrates the quality of and highlights boundaries for the solution. 
	\item Produce a scientific text of fair quality both textually and scientifically.
	\item The student must be able to make an oral presentation of own work.
\end{enumerate}
Project specific learning goals:
\begin{enumerate}
    \item Implement local adaptive optimization of timesteps (LAOT)
	\item Evaluate LAOT to minimize the risk of unwanted deformations in grids
        and minimize the computational cost.
    \item Discuss how LAOT is performed in practice using existing 2nd order optimization methods.
\end{enumerate}

@@

\subsection{Problem Statement}
Study the application of locally adaptive timestepping in 1 dimensional
simulation of a mass spring system.

@@

\subsection{Proposed solution}
We wish to develop a method for locally adapting the timestep size in
order to avoid curl ups/explosions while still maintaining the original
timestep size of the rest of the simulation. In other words for each of
the original timesteps we perform further simulations of problematic local
areas of the grid with smaller timesteps.

>>>>

\section{Problem Statement}
Study the application of locally adaptive timestepping in 1 dimensional
simulation of a mass spring system.

\section{Learning Goals}
Course specific learning goals:
\begin{enumerate}
	\item Formulate an operational project plan.
	\item Search the relevant literature and write a literature review setting own work in perspective.
	\item Be able to formulate what plagiarism is, and demonstrate proper citation and reference style.
	\item Solve a selected problem of fair Computational and Mathematical Modelling / eScience content and difficulty.
	\item Produce a thorough experiment plan that clearly demonstrates the quality of and highlights boundaries for the solution. 
	\item Produce a scientific text of fair quality both textually and scientifically.
	\item The student must be able to make an oral presentation of own work.
\end{enumerate}
Project specific learning goals:
\begin{enumerate}
    \item Implement local adaptive optimization of timesteps in a 1
dimensional mass-spring system
    \item Develop and implement possible heuristics for use in LAOT schemes
	\item Evaluate LAOT to minimize the risk of unwanted deformations in grids
        and minimize the computational cost.
    \item Discuss the use and combination of LAOT schemes and heuristics based
        on the evaluation of these
\end{enumerate}

@@

@@

\subsection{Proposed solution}
We wish to develop a method for locally adapting the timestep size (either
spatial or in time) in
order to avoid curl ups/explosions for minimizing the number of computations
needed for a simulation. We do this by exploring possible methods and heuristics
for LAOT application without affecting the outcome of a standard simulation.
